---
output:
  html_document: default
  pdf_document: default
---
```{r}
#Question 1
library(gbm)
library(plyr)
library(MLmetrics)
library(Hmisc)
library(tidyverse);
library(Rtsne);
data <- read_csv("500_Person_Gender_Height_Weight_Index.csv")
head(data)

```
```{r}
smp_size <- floor(0.75 * nrow(data))

## set the seed to make your partition reproducible
set.seed(100)
train_ind <- sample(seq_len(nrow(data)), size = smp_size)

train <- data[train_ind, ]
test <- data[-train_ind, ]
test
```
```{r}
#training_data$Classification <- as.factor(training_data$Classification)
model <- glm(as.factor(Gender) ~ Height +
                 Weight,family=binomial(link='logit'),data=train)
pred <- predict(model, newdata=test, type="response");
sum(pred>0.5)/nrow(test)
```

```{r}
#questoin 2
person_info2 <- read_csv("500_Person_Gender_Height_Weight_Index.csv")
person_info2$Gender = factor(person_info2$Gender, 
                        levels = c("Male","Female"),
                        labels = c(0,1))

person_info2$Gender <- as.character(person_info2$Gender)
head(person_info2)

smp_size2 <- floor(0.75 * nrow(person_info2))

## set the seed to make your partition reproducible
set.seed(100)
train_ind2 <- sample(seq_len(nrow(person_info2)), size = smp_size2)

train2 <- person_info2[train_ind2, ]
test2 <- person_info2[-train_ind2, ]
```
```{r}
train2
model2 <- gbm(Gender ~ Height + Weight,distribution="bernoulli",data=train2,
             n.trees = 100,
             interaction.depth = 2,
             shrinkage = 0.1);
pred2 <- predict(model2, newdata = test2, type="response");

sum(pred2>0.5)/nrow(test2)
```
```{r}
#question 3
data2 = read_csv("500_Person_Gender_Height_Weight_Index.csv")
data2 <- data2 %>%
    filter(Gender == 'Female')
data3 = read_csv("500_Person_Gender_Height_Weight_Index.csv")

data3 <- data3 %>%
    filter(Gender == 'Male')%>%head(50)

data4 = rbind(data2,data3)
data4$Gender = factor(data4$Gender, 
                        levels = c("Male","Female"),
                        labels = c(0,1))
```
```{r}
smp_size <- floor(0.75 * nrow(data4))

## set the seed to make your partition reproducible
set.seed(100)
train_ind <- sample(seq_len(nrow(data4)), size = smp_size)

train <- data4[train_ind, ]
test <- data4[-train_ind, ]
```

```{r}
model3 <- glm(Gender ~ Height +
                 Weight,family=binomial(link='logit'),data=train)
pred <- predict(model3, newdata=test, type="response");
```
```{r}
pred <- as.numeric(pred)
test$Gender = as.numeric(test$Gender)
f1 <- MLmetrics::F1_Score;
pred[10] <- 0
f1(test$Gender,as.numeric(pred>0.5))
#my model always predict true. 
```

```{r}
#question 4 
ggplot(tibble(p_gender=pred),aes(p_gender)) + geom_density() + geom_vline(xintercept=0.5);
roc <- do.call(rbind, Map(function(threshold){
    p <- pred > threshold;
    tp <- sum(p[test$Gender])/sum(test$Gender);
    fp <- sum(p[!test$Gender])/sum(!test$Gender);
    tibble(threshold=threshold,
           tp=tp,
           fp=fp)
},seq(100)/100))

ggplot(roc, aes(fp,tp)) + geom_line() + xlim(0,1) + ylim(0,1) +
    labs(title="ROC Curve",x="False Positive Rate",y="True Positive Rate");
```
4. The ROC curve is the Plot of True Positive Rate against False Postive Rate. The area under the curve is a good threshold-free estimate of the performance of the classifier.




```{r}

source("utils.R");
data5 <- read_csv("500_Person_Gender_Height_Weight_Index.csv") 

data5$Gender = factor(data5$Gender, 
                        levels = c("Male","Female"),
                        labels = c(0,1))
```


```{r}
cc <- kmeans(data5, 4);
fit <- Rtsne(data5, dims = 2,check_duplicates = FALSE);
ggplot(fit$Y %>% as.data.frame() %>% as_tibble() %>% mutate(label=cc$cluster),aes(V1,V2)) +
    geom_point(aes(color=factor(label)));
```
```{r}
cc$centers
```
5)There are some clusters in the right and left based on the plot. Based on the centers of the clusters, male tend to have a larger height and larger weight. Female tend to have a lower height and lower weight. So label 1 can be a female with low height and weight. label 2 can be a male with high height and high weight. 
